SDR enhancement by clouds

### 2024-03-20 article/article.Rmd
Commit 2024-03-20 12:14

We computed the daily trend of the mean over irradiance of CE (Figure\ 
\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
using the 'maximum likelihood' fitting method [@Gardner1980; @Jones1980] by
implementing the function 'arima' from the library 'stats' of the R programming
language [@RCT2023]. The trends were reported together with the $2\sigma$ error.
We observe an increase of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2$
on the mean over irradiance.

@@

Another interesting aspect of the CE cases, is the seasonal cycle. In Figure\ 
\ref{fig:relative-month-occurancies}, we have the box plot (whisker plot), where the
values have been normalized by the highest median value, that occurs in May.
Although the number of occurrences has a wide spread throughout the study period,
the most active period of CE occurrences is during May and June. During the Winter
(December -- February) the CE cases are about 25% of the maximum. The rest of the
months the occurrences seems to ramp between the maximum and minimum.

@@

```{r echo=FALSE, fig.cap="Distribution of CE over irradiance"}
knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
```

@@

>>>>

We computed the daily trend of the mean over irradiance of CE (Figure\nobreakspace{}
\ref{fig:CEmeanDaily}), using a first-order autoregressive model with lag of 1 day,
using the 'maximum likelihood' fitting method [@Gardner1980; @Jones1980] by
implementing the function 'arima' from the library 'stats' of the R programming
language [@RCT2023]. The trends were reported together with the $2\sigma$ error.
We observe an increase of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2$
on the mean over irradiance.

@@

Another interesting aspect of the CE cases, is the seasonal cycle. In
Figure\nobreakspace{} \ref{fig:relative-month-occurancies}, we have the box plot
(whisker plot), where the values have been normalized by the highest median value,
that occurs in May.  Although the number of occurrences has a wide spread throughout
the study period, the most active period of CE occurrences is during May and June.
During the Winter (December -- February) the CE cases are about 25% of the maximum.
The rest of the months the occurrences seems to ramp between the maximum and minimum.

@@

The distribution of the CE over irradiance spreads uniformly Figure\nobreakspace{}
\ref{fig:ovir-distribution}. Where there is an inverse relation  between the events
frequency and events intensity . This is expected as, the stronger the CE events
become, the more rare is the atmospheric and sun conditions to occur.

```{r ovir-distribution, echo=FALSE, fig.cap="Distribution of CE over irradiance"}
knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
```

@@

In order to further study the characteristics of the CE events, we grouped the singe
minute CE events, to continuous CE.

### 2024-03-20 article/article.tex
Commit 2024-03-20 12:14

\ldots{} (\textbf{Zhang2018?}) \ldots.

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/P-groups-bin2d-1}

@@

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-6}
\end{figure}

>>>>

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/groups-4}

@@

{\centering \includegraphics[width=0.7\linewidth]{../images/groups-8}

\caption{Relation of maximun over irradiance and CE group duration}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Distribution of the number of ECE cases}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-6}
\end{figure}

{\centering \includegraphics[width=0.7\linewidth]{../images/extremedistributions-4}

\caption{Distribution of ECE Irradiance above 'TSI'}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Distribution of }\label{fig:unnamed-chunk-8}
\end{figure}
